\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large Krish Suchak}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (201) 893-6487       \hfill LinkedIn: \url{https://linkedin.com/in/suchak1} \\
    \noindent Email: suchak@uchicago.edu  \hfill Github: \url{https://github.com/suchak1} \vspace{0mm}\\\vspace{-4.5mm}

    \section{\mysidestyle Education}

    \textbf{University of Chicago}, Chicago, IL \vspace{2mm}\\\vspace{1mm}%
    \textsl{BS, Computer Science} \hfill Expected Graduation: \textbf{June 2020}\\
    Received highest honors for senior thesis analyzing over 200,000 Chinese
    blog posts, algorithmically detecting mutations in the Chinese language in
    response to censorship. Completed coursework in abstract algebra,
    Galois theory, topology, real and complex analysis, probability theory, and
    linguistics.

    \section{\mysidestyle Professional\\Experience}

    \textbf{Chicago Transit Authority}, Chicago, IL \vspace{2mm}\\\vspace{1mm}%
    \textsl{Data Science Intern} \hfill \textbf{Sep 2019 -- Apr 2020}

    \begin{itemize}
\item Created a dynamic, color-coded scatter plot  of rail stations vs arrival times, so that color strength of points correspond to lateness of trains. \hfill Tools: JS/Python, plotly

\item Corrected headway calculations for time between trains since database occasionally contains incorrect values. \hfill Tools: Python, pandas

\item Generated automatic rail observations emails based on SQL query results (pandas).

    \end{itemize}
    
    \hfill Tools: Python + pandas, Javascript, SQL

    \textbf{Virtru}, Washington, DC \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{Feb 2017 -- present}\\
    A SaaS business intelligence product to help analysts enrich their customer
    data with geographic columns (latitudes/longitudes, ZIP codes, etc) and
    demographics. Processing is server-based but integrated with Microsoft
    Excel, Python, and the Domo platform: \url{www.cairngeographics.com}.

    \textbf{Google}, Venice, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer III} \hfill \textbf{Jun 2014 -- Mar 2016}\\
    Worked on a small team using natural language processing and other machine
    learning techniques to improve advertisement quality. Led a 20\% project
    related to mining semantic information from web data, which was adopted by
    several teams across different product areas. Built a named entity
    recognition system in C++ and a link detection algorithm that runs on very
    large graphs; contributed to a topic model for clustering semantic entities.

    \textbf{Whisper}, Venice, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer and Data Scientist} \hfill \textbf{Mar 2013 -- Apr 2014}\\
    Sole data scientist at a rapidly expanding social media startup
    seeing upwards of three billion monthly pageviews. Designed and built an NLP
    service to extract topics and tags from posts, predict image searchterms
    from unstructured text, and target content to users. Implemented a new
    geographic search system using PostGIS that decreased search time by
    90\%. Worked closely with the front and backend development teams, writing
    production code in Erlang and Python.


    \section{\mysidestyle Programming\\Experience}

    \emph{Languages:} Python, Javascript / React, Bash, Java, Racket, C++, C, \LaTeX \\
    \emph{Data Technology:} Cassandra, Redis, PostgreSQL, ElasticSearch/Lucene, MySQL, MongoDB
\end{resume}
\end{document}
