\documentclass[margin]{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{unicode-math}
\usepackage[dvipsnames]{xcolor}

\definecolor{blu}{RGB}{15, 165, 227}
\definecolor{maroon}{RGB}{220, 85, 110}

\begin{document}
%\name{\Large Krish Suchak}
\centerline{\textbf {\Large Krish Suchak}}
\centerline{900 Summerbrooke Drive $\smwhtdiamond$ Tallahassee, FL 32312 $\smwhtdiamond$ 201-893-6487 $\smwhtdiamond$ \texttt{\href{mailto:suchak@uchicago.edu}{suchak@uchicago.edu}}}
\vspace{3mm}
%\fullline \vspace{2mm} 
\hrule
\vspace{1mm}
\centerline{\texttt{\href{https://github.com/suchak1}{github.com/suchak1}} \hspace{10mm} | | \hspace{10mm} \texttt{\href{https://linkedin.com/in/suchak1}{linkedin.com/in/suchak1}}}

    \section{\mysidestyle Education}

    \textcolor{maroon}{\textbf{University of Chicago}}, Chicago, IL \hfill Expected Graduation: \textbf{June 2020} \vspace{2mm}\\\vspace{1mm}%
    \textsl{BS, Computer Science} \hfill SAT: 1550/1600\\
Scholarships: \textit{University Scholar $\smwhtdiamond$ Dean’s Scholar $\smwhtdiamond$ National Merit Scholar}\\
Relevant Coursework: \textit{Software Construction, Data Science for CS, Cryptocurrencies, Algorithms}

    \section{\mysidestyle Professional\\Experience}

    \textcolor{blu}{\textbf{Chicago Transit Authority}}, Chicago, IL \vspace{2mm}\\\vspace{1mm}%
    \textsl{Data Science Intern} \hfill \textbf{Sep 2019 -- Apr 2020}

    \begin{itemize}
\item Created a dynamic, color-coded scatter plot  of rail stations vs arrival times, so that color strength of points correspond to lateness of trains. \hfill \textit{Javascript \& Python, plotly}

\item Corrected headway calculations for time between trains, bypassing incorrect database values. \\ ▪ \hfill \textit{Python, pandas}

\item Generated automatic rail observations based on database query results. \hfill \textit{SQL, Redshift}

    \end{itemize}
    
    \textcolor{blu}{\textbf{Virtru}}, Washington, DC \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{Jun 2019 -- Aug 2019}

\begin{itemize}
\item Added new components and fixed bugs in front-end Dashboard project. \hfill \textit{Javascript / React}
\item Wrote scripts to automate retrials of tests and fetch parameters from AWS SSM. \hfill \textit{Bash}
\item Fixed customer-facing export client for JSON and CSV data. \hfill \textit{Python}
\end{itemize}


    \section{\mysidestyle Awards}
    \begin{itemize}
    \item
    \textcolor{blu}{\textbf{1st place (\$15k)}} -- Virtru Privacy Engineering Challenge (\textbf {Audit Map} project) \hfill \textbf{Nov 2019} \\ \url{https://www.virtru.com/blog/privacy-engineering-challenge-winner-2019/}
    \item
\textbf{National Merit Scholar}, Dean’s Scholar, University Scholar \hfill \textbf{2014 -- 2020} %\url{www.tallahassee.com/story/news/2014/05/07/national-merit-scholars-announced/8808739/}
\item
\textbf{CAAP Scholar} (Chicago Academic Achievement Program) \hfill \textbf{2014 -- 2020}
\end{itemize}
    \section{\mysidestyle Projects}
    \begin{itemize}
\item \textcolor{blu}{\textbf{Audit Map}} \hfill \textbf{2019}

1st place (\$15,000 cash prize) winning entry for Virtru Privacy Engineering Challenge \\ 
Enables tracking and retroactive revocation of access to encrypted files remotely from map view. 

\url{https://github.com/suchak1/audit_map} \hfill \textit{Javascript / React, Mapbox}

\item \textbf{IntraVideo Search} \hfill \textbf{2019}

A search engine for video, leveraging ML image classification and concurrent multiprocessing. Led team of 8 and proposed concept.\\ Input: source video and search terms \hfill Output: relevant clips from source video

\url{https://github.com/suchak1/intravideo_search} \hfill \textit{Python}

\item \textbf{Crypto (WIP - currently redoing in Python)} \hfill \textbf{2016, 2019}

Cryptocurrency portfolio data collection, graphic visualization, and predictive models.

Involves API calls, XML parsing, and automated data collection.

\url{https://github.com/suchak1/crypto} \hfill \textit{Javascript}

    \end{itemize}
        \section{\mysidestyle Programming\\Experience}

    \emph{Languages:} $\overline{\mbox{Python, Javascript / React, Bash}}$, Java, Racket, C++, C, \LaTeX \\
    \emph{Tools:} Agile [Jira], Git [Github, Bitbucket], AWS, Continuous Integration [Buildkite, Travis CI]
    
\textbf {\textit {Note:}} All links are clickable on PDF.
    
\end{document}
